### 2022-01-31 chapters/sctld/article.tex
slim+swan paper added
removed duplicated ref

The mesh resolution depended only on the distance to the coast, but we distinguished between the coastlines along the FRT where we imposed a maximum resolution of 100 m and the other coastlines along which the finest resolution was 2500 m. The mesh was generated with the open-source mesh generator GMSH \citep{Geuzaine2009} and is composed of approximately $7 \times 10^5$ elements. The coarsest elements, far away from the FRT, had a characteristic length size of about 10 km. Fig. \ref{fig:setup} depicts how a 100-m spatial resolution mesh simulated fine-scale details of the ocean currents, such as recirculation eddies and currents within the dense reef system in the Lower Keys that consist of many individual reefs with narrow passages in between.

@@

\begin{figure}
    \centering
    \includegraphics[width=.8\textwidth]{chapters/sctld/figures/sctld_validation_corrected.jpg}
    \caption{Summary of epidemiological model simulations with calibrated transmission parameters. \textbf{Top:} Modeled disease front speed for each type of current with respect to intra-reef 'infection' threshold $I_0$. \textbf{Bottom:} Mean distance between predicted diseased reefs and observed disease points. These results show that mean barotropic currents outperformed other modes of transport at reproducing the observed spread of the disease. The appearance of a plateau suggests that the modeled spread of the disease occurs for a well-defined range of values of $I_0$.}
    \label{fig:results}
\end{figure}

>>>>

The mesh resolution depended only on the distance to the coast, but we distinguished between the coastlines along the FRT where we imposed a maximum resolution of 100 m and the other coastlines along which the finest resolution was 2500 m. The mesh was generated with the open-source mesh generator GMSH \citep{geuzaine2009gmsh} and is composed of approximately $7 \times 10^5$ elements. The coarsest elements, far away from the FRT, had a characteristic length size of about 10 km. Fig. \ref{fig:setup} depicts how a 100-m spatial resolution mesh simulated fine-scale details of the ocean currents, such as recirculation eddies and currents within the dense reef system in the Lower Keys that consist of many individual reefs with narrow passages in between.

@@

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{chapters/sctld/figures/sctld_validation_corrected.jpg}
    \caption{Summary of epidemiological model simulations with calibrated transmission parameters. \textbf{Top:} Modeled disease front speed for each type of current with respect to intra-reef 'infection' threshold $I_0$. \textbf{Bottom:} Mean distance between predicted diseased reefs and observed disease points. These results show that mean barotropic currents outperformed other modes of transport at reproducing the observed spread of the disease. The appearance of a plateau suggests that the modeled spread of the disease occurs for a well-defined range of values of $I_0$.}
    \label{fig:results}
\end{figure}
